data_cleaning_longer_period

### 2023-08-21 code/data_cleaning_longer.Rmd
updated code, moving toward figures
adding payor to TE*Dist estimates

library(did2s)

@@

@@

for(i in 2:length(locs)){
  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes")[,c(1:5, 10)]

  colnames(temp.zip) <- new.zip.names
  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(ZipCode = str_pad(ZipCode, 5, pad = "0")))
}

uds.zip$ReportingYear <- as.numeric(uds.zip$ReportingYear)
uds.zip$NumberofPatients <- as.numeric(uds.zip$NumberofPatients)

uds.zip[is.na(uds.zip$NumberofPatients),]$NumberofPatients <- 0

@@

@@

## Read in census data for all zip codes
```{r}
library(tidycensus)

@@

for (i in 1:10){
  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
                                     "B03001_003", 
                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
                                     "B23025_002","B23025_005",
                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
                       year = 2011 + i) %>% 
  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
    mutate(YEAR = 2009 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
           Male = B01001_002, Female = B01001_026, 
           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
           Hispanic = B03001_003, 
           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
           Unemployed = B23025_005, Unemp_denom = B23025_002,
           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1 ) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities)

>>>>

library(did2s)
library(tidycensus)

@@

uds.zip <- cbind(uds.zip, "Uninsured" = NA ,  "Medicaid" = NA, "Medicare" = NA, "Private" = NA)

@@

for(i in 2:length(locs)){
  temp.zip <- read_excel(locs[i], sheet = "HealthCenterZipCodes") #[,c(1:5, 10)]

  colnames(temp.zip) <- new.zip.names[c(1:5, 7:10, 6)]
  uds.zip <- rbind(uds.zip, temp.zip %>% mutate(ZipCode = str_pad(ZipCode, 5, pad = "0")))
}

uds.zip$ReportingYear <- as.numeric(uds.zip$ReportingYear)
uds.zip$NumberofPatients <- as.numeric(uds.zip$NumberofPatients)
uds.zip$Uninsured <- as.numeric(uds.zip$Uninsured)
uds.zip$Medicaid <- as.numeric(uds.zip$Medicaid)
uds.zip$Medicare <- as.numeric(uds.zip$Medicare)
uds.zip$Private <- as.numeric(uds.zip$Private)

uds.zip[is.na(uds.zip$NumberofPatients),]$NumberofPatients <- 0
uds.zip[is.na(uds.zip$Uninsured) & uds.zip$ReportingYear > 2012,]$Uninsured <- 0
uds.zip[is.na(uds.zip$Medicaid) & uds.zip$ReportingYear > 2012,]$Medicaid <- 0
uds.zip[is.na(uds.zip$Medicare) & uds.zip$ReportingYear > 2012,]$Medicare <- 0
uds.zip[is.na(uds.zip$Private) & uds.zip$ReportingYear > 2012,]$Private <- 0

@@

uds.zip

@@

## Read in census data for all zip codes
```{r}

@@

for (i in 1:10){
  census <- rbind(census, get_acs(geography = "zcta", survey = "acs5",
                       variables = c("B01003_001","B17001_001","B17001_002","B01001_002","B01001_026",
                                     "B02001_002","B02001_003","B02001_004","B02001_005","B02001_006","B02001_008",
                                     "B03001_003", 
                                     "B01001_003","B01001_004","B01001_005","B01001_006","B01001_007","B01001_008","B01001_009",
                                     "B01001_010","B01001_011","B01001_013","B01001_014","B01001_015","B01001_016","B01001_017",
                                     "B01001_018","B01001_019","B01001_020","B01001_021","B01001_022","B01001_023","B01001_024","B01001_025",
                                     "B01001_027","B01001_028","B01001_029","B01001_030","B01001_031","B01001_032","B01001_033","B01001_034",
                                     "B01001_035","B01001_036","B01001_037","B01001_038","B01001_039","B01001_040","B01001_041","B01001_042","B01001_043",
                                     "B01001_044","B01001_045","B01001_046","B01001_047","B01001_048","B01001_049",
                                     "B06009_002","B06009_003", "B06009_004","B06009_005","B06009_006",
                                     "B23025_002","B23025_005",
                                     "C27007_001", "C27007_004", "C27007_007", "C27007_010", "C27007_014", "C27007_017", "C27007_020",
                                     "B18135_001","B18135_007","B18135_012","B18135_018","B18135_023","B18135_029","B18135_034"), 
                       year = 2011 + i) %>% 
  pivot_wider(id_cols = c(GEOID, NAME), names_from = variable, values_from = estimate) %>% 
    mutate(YEAR = 2011 + i, TotalPop = B01003_001, PovertyStatusDet = B17001_001, IncomeBelowPoverty = B17001_002,
           AgeUnder18 = B01001_003 + B01001_004 + B01001_005 + B01001_006 + B01001_027 + B01001_028 + B01001_029 + B01001_030,
           Age18to64 = B01001_007 + B01001_008 + B01001_009 + B01001_010 + B01001_011 + B01001_013 + B01001_014 + B01001_015 + 
                       B01001_016 + B01001_017 + B01001_018 + B01001_019 + B01001_031 + B01001_032 + B01001_033 + B01001_034 +
                       B01001_035 + B01001_036 + B01001_037 + B01001_038 + B01001_039 + B01001_040 + B01001_041 + B01001_042 + B01001_043, 
           Age65andOver = B01001_020 + B01001_021 + B01001_022 + B01001_023 + B01001_024 + B01001_025 + 
                          B01001_044 + B01001_045 + B01001_046 + B01001_047 + B01001_048 + B01001_049, 
           Male = B01001_002, Female = B01001_026, 
           White = B02001_002, Black = B02001_003, AIAN = B02001_004, Asian = B02001_005 + B02001_006, MR = B02001_008, 
           Hispanic = B03001_003, 
           EducLow = B06009_002, EducMid = B06009_003 + B06009_004, EducHigh = B06009_005 + B06009_006,
           Unemployed = B23025_005, Unemp_denom = B23025_002,
           MCD.denom = C27007_001	, Medicaid = C27007_004	 + C27007_007 + C27007_010	+ C27007_014 + C27007_017 + C27007_020,
           Unins.denom = B18135_001, Uninsured = B18135_007 + B18135_012 + B18135_018 + B18135_023 + B18135_029 + B18135_034) %>% 
    select(ZipCode = GEOID, NAME, YEAR, TotalPop:Uninsured))

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  filter(`2010` == 1 & `2011` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, 
               Efficiency = ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities)
